Intrinsic Verification of Parsers and Formal Grammar Theory in Dependent Lambek Calculus

### 2024-11-10 paper/paper.tex
author order
generalize adamek

\max{TODO: spelling}
\begin{theorem}[Adamek]
  If a functor $F : \mathcal C \to \mathcal C$ preserves
  $\omega$-colimits and $\mathcal C$ has an initial object and
  $\omega$-colimits, then $F$ has an initial algebra given by the
  colimit of the chain
  \[ 0 \to F(0) \to F(F(0)) \to \cdots \]
\end{theorem}

>>>>

\max{TODO: spelling}
\begin{theorem}[Adamek]
  If a functor $F : \mathcal C \to \mathcal C$ preserves all 
  $\kappa$-colimits and $\mathcal C$ has an initial object and
  $\kappa$-colimits, then $F$ has an initial algebra given by the
  colimit of the chain
  \[ 0 \to F(0) \to F(F(0)) \to \cdots \]
\end{theorem}
